\Huge ACM and Climate Change

### 2019-05-28 main.tex
Fix build
Tidy

A broad scientific consensus warns that the earth is warming, due to human
emissions of carbon dioxide and other greenhouse gases (Figure
\ref{fig:warming}). This is not a problem we can leave to future
generations: we are up against it now. Indeed, the UN's Intergovernmental
Panel on Climate Change (IPCC) recently recommended a 40\% decrease in
emissions by 2030 to avoid irreversible damage
(Figure~\ref{fig:IPCC-cover}). Achieving reductions on this scale will
require urgent and sustained commitment at all levels of society, including
non-governmental communities such as universities, companies, and scientific
societies like ACM.

Why ACM? Because one of ACM's main activities is organizing international
conferences, which produce significant emissions of greenhouse gases,
particularly from air travel. For example, a single round-trip flight from
Philadelphia to Paris emits the equivalent of about 1.7 tons of carbon
dioxide (\COtwoE) per passenger~\cite{carboncalculator}\iflater\bcp{Trim
  citation?}\fi---a substantial fraction of the {\em total} yearly emissions
for an average resident of the US (16.5 tons) or Europe (7
tons)~\cite{emissions}.  \iflater\bcp{For comparison, ...  (put in some
  figures about the footprints of a few other things that people might think
  of reducing---driving, eating meat, upgrading their fridge...)}\fi{}
Moreover, these emissions have no near-term 
technological fix because jet fuel is difficult to replace with
renewable energy sources~\cite{elec-air}. 
\iflater\bcp{Trimmed this sentence: Reducing the \COtwoE{} footprint
of conferences will require a reduction in the footprint of the attendees'
air travel.}\fi

Obviously, conferences also create value.  Science is a fundamentally social
process, and the conference system accelerates research through
opportunities for high-bandwidth interaction, direct dissemination of
results, network building, and serendipitous cross-fertilization.

This creates a dilemma: How do we weigh the environmental harm caused by
conference travel against the social benefits of the scientific progress
that comes from conferences?  This seems an extremely difficult question to
answer: the harm and the compensating benefits cannot be directly
compared---they are apples and oranges.
%
Fortunately, we have a well-established mechanism for comparing apples and
oranges---indeed, for comparing almost anything: the magic of markets.  By
mapping choices to currency amounts, markets facilitate individual valuation
of costs and benefits across vastly different activities.\bcp{Give a simple,
  concrete example.} For this reason, many policy experts advocate some form
of carbon pricing, which places a monetary cost on greenhouse gas emissions,
giving a market signal that changes aggregate behavior.\bcp{See
  https://kleinmanenergy.upenn.edu/policy-digests/why-carbon-pricing-falls-short
for lots of good phrasing and citations.}
Exactly what the
cost should be is a challenging question, but it has a clear ``success
criterion'': The cost should be set so that the world arrives at zero
emissions within the timeframe that climate scientists tell us is safe.

@@

Finally, we can start imposing a cost on ourselves by using carbon
offsets.  
\begin{itemize}
\item There are two good reasons for doing this, as well as some significant
concerns.
\item Concern:
Organizations are not set up to do it.  Our experience with getting
ACM to introduce an offsetting policy shows that it requires significant
effort.
\item Concern: It is hard to choose the price (right now there is an oversupply), and
setting it too low leads to complacency --- it doesn't really bite, so it
doesn't change people's behavior
\end{itemize}
\item This issue leads many people to argue that offsets "let people off the hook" and encourage
inaction, but we believe it is consistent with encouraging action -- again,
if offsets are priced right.
\item Moreover, offsets are an effective way to reduce carbon emissions {\em
  now}.  (Yes, there are bogus ones, but not all are bogus.)
\item Most importantly, it is the right thing to do: We should be changing
our behavior starting now, and giving ourselves a (correct) ``price signal''
is an effective way to achieve this.
\end{itemize}

@@

\bcp{Things still missing:
  \begin{itemize}
  \item citations for the claims we make
  \item an excuse for citing the Climate Committee report and perhaps
  mentioning other SIGPLAN activities
  \item Decide what figures we want, if any
  \item go through all the suggestions below and in the referee reports,
  once more
  \item Write a cover letter
  \begin{itemize}
  \item We tried hard to remove all incrementalism and make it much more
  hard hitting
  \item However, we did keep the suggestion of carbon offsets, hopefully
  in a more convincing / palatable / better argued form
  \item what else?
  \end{itemize}
  \end{itemize}
}

@@

\item \item 

>>>>

A broad scientific consensus warns that the earth is warming, due to human
emissions of carbon dioxide and other greenhouse gases (Figure
\ref{fig:warming}). This is not a problem we can leave to future
generations: we are up against it now. The UN's Intergovernmental
Panel on Climate Change (IPCC) recently recommended a 40\% decrease in
emissions by 2030 to avoid irreversible damage
(Figure~\ref{fig:IPCC-cover}). Achieving reductions on this scale will
require urgent and sustained commitment at all levels of society, including
non-governmental organizations such as universities, companies, and scientific
societies like ACM.

Indeed, ACM arguably has an especially important role to play, since one of
its main activities is organizing international
conferences, which produce significant emissions of greenhouse gases,
particularly from air travel.   A single round-trip flight from
Philadelphia to Paris emits the equivalent of about 1.7 tons of carbon
dioxide (\COtwoE) per passenger~\cite{carboncalculator}\iflater\bcp{Trim
  citation?}\fi---a substantial fraction of the {\em total} yearly emissions
for an average resident of the US (16.5 tons) or Europe (7
tons)~\cite{emissions}.  \iflater\bcp{For comparison, ...  (put in some
  figures about the footprints of a few other things that people might think
  of reducing---driving, eating meat, upgrading their fridge...)}\fi{}
Moreover, these emissions have no near-term 
technological fix because jet fuel is difficult to replace with
renewable energy sources~\cite{elec-air}. 
\iflater\bcp{Trimmed this sentence: Reducing the \COtwoE{} footprint
of conferences will require a reduction in the footprint of the attendees'
air travel.}\fi

On the other hand, conferences obviously also create value.  Science is a
fundamentally social process, and the conference system accelerates research
through opportunities for high-bandwidth interaction, direct dissemination
of results, network building, and serendipitous cross-fertilization.

This leads to a puzzle: How do we weigh the environmental harm caused by
conference travel against the social benefits of the scientific progress
that comes from conferences?  This seems an extremely difficult question to
answer: the harm and the compensating benefits cannot be directly
compared---they are apples and oranges.
%
Fortunately, there is a well-established mechanism for comparing apples and
oranges---indeed, for comparing almost anything: the magic of markets.  By
mapping choices to currency amounts, markets facilitate individual valuation
of costs and benefits across vastly different activities.\bcp{Give a simple,
  concrete example.} For this reason, many policy experts advocate some form
of carbon pricing, which places a monetary cost on greenhouse gas emissions,
giving a market signal that changes aggregate behavior.\bcp{See
  https://kleinmanenergy.upenn.edu/policy-digests/why-carbon-pricing-falls-short
for lots of good phrasing and citations.}
Exactly what the
cost should be is a challenging question, but it has a clear ``success
criterion'': The cost should be set so that the world arrives at zero
emissions within the timeframe that climate scientists tell us is safe.

@@

Finally, we can start imposing a cost on ourselves by using carbon
offsets.  
\begin{itemize}
\item There are two good reasons for doing this, as well as some significant
concerns.
\item Concern:
Organizations are not set up to do it.  Our experience with getting
ACM to introduce an offsetting policy shows that it requires significant
effort.
\item Concern: It is hard to choose the price (right now there is an oversupply), and
setting it too low leads to complacency --- it doesn't really bite, so it
doesn't change people's behavior
\item This issue leads many people to argue that offsets "let people off the hook" and encourage
inaction, but we believe it is consistent with encouraging action -- again,
if offsets are priced right.
\item Moreover, offsets are an effective way to reduce carbon emissions {\em
  now}.  (Yes, there are bogus ones, but not all are bogus.)
\item Most importantly, it is the right thing to do: We should be changing
our behavior starting now, and giving ourselves a (correct) ``price signal''
is an effective way to achieve this.
\end{itemize}

@@

\bcp{Things still missing:
  \begin{itemize}
  \item citations for the claims we make
  \item an excuse for citing the Climate Committee report and perhaps
  mentioning other SIGPLAN activities
  \item Decide what figures we want, if any
  \item go through all the suggestions below and in the referee reports,
  once more
  \item Think about adding headings, per Bishop's recommendation
  \item Go through all the comments and ideas below (including the CACM
  reviews) one last time
  \item Change to a catchier title (``so something more personal such as
  "Your conference trip and climate change" might get more readers'') 
  \item Write a cover letter
  \begin{itemize}
  \item We tried hard to remove all incrementalism and make it much more
  hard hitting
  \item However, we did keep the suggestion of carbon offsets, hopefully
  in a more convincing / palatable / better argued form
  \item what else?
  \end{itemize}
  \end{itemize}
}

@@
